### 2021-06-01 paper/model_validation.tex
Bring paper up to date for CRC Discussion Series. (#2)
Co-authored-by: Tobias Raabe <raabe@posteo.de>
Add fitness plots.

We validate our model in two ways: 1) We look at the in-sample fit over the estimation
period. 2) We look at the out-of-sample fit for November. The last one is a challenging
test for our model because there was a strong policy change between the estimation
period and November. The model convincingly passes both tests.

\subsection{In-Sample Fit}
\label{sub:in_sample_fit}

Despite fitting only four infection probabilities, the in-sample fit is very good.
The best fit is achieved in the largest age groups.
This is so mechanically, because we weigh the
deviations between simulated and observed infection rates by group sizes. The worst fit
is achieved for the 80 to 100 years old.
There are three reasons for this: Firstly, we only model private households at
the moment, meaning that nursing homes are not part of the synthetic population we
simulate. Since community housing residents are part of the German Mikrozensus
\citep{FDSAeDBUDL2018} which forms the basis for our synthetic population, we can and
plan to include community housing residents in the near future.
Secondly, the elderly, especially nursing home residents, are tested more often than
the general population leading to more cases being detected in this age group.
We are currently working to include age-variant testing strategies,
using \href{https://ars.rki.de/Content/COVID19/Main.aspx}{data by the RKI}
\citep{Seifried2020}.

\begin{figure}[h]
    \centering
    \includegraphics[width=1.1\textwidth]{../figures/goodness_of_fit_by_age_group}
    \caption{Reported vs. simulated weekly incidence rates of infections.}
    \label{fig:goodness_of_fit}
    \figurenotes{
        The figure shows the weekly incidence rates per 100,000 people for the reported
        (red line) versus the simulated infections rates (blue line) for age groups
        available in the data provided by the Robert-Koch Institut.
    }
\end{figure}

>>>>

This compares simulated data from our model with empirical data from Germany. We at
observed infections, fatality rates, the spread of the B117 mutation, vaccinations and
rapid test demands. Where available we do not only look at aggregated statistics but
also analyze the model fit for age groups.

\textcolor{red}{summarize the fit}

\subsection{Observed Infections}
\label{sub:in_sample_fit}

% Despite fitting only four infection probabilities, the in-sample fit is very good.
% The best fit is achieved in the largest age groups.
% This is so mechanically, because we weigh the
% deviations between simulated and observed infection rates by group sizes. The worst fit
% is achieved for the 80 to 100 years old.
% There are three reasons for this: Firstly, we only model private households at
% the moment, meaning that nursing homes are not part of the synthetic population we
% simulate. Since community housing residents are part of the German Mikrozensus
% \citep{FDSAeDBUDL2018} which forms the basis for our synthetic population, we can and
% plan to include community housing residents in the near future.
% Secondly, the elderly, especially nursing home residents, are tested more often than
% the general population leading to more cases being detected in this age group.
% We are currently working to include age-variant testing strategies,
% using \href{https://ars.rki.de/Content/COVID19/Main.aspx}{data by the RKI}
% \citep{Seifried2020}.

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/comparisons/fall_fit/full_new_known_case}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/comparisons/spring_fit/full_new_known_case}
\end{subfigure}
\caption{Simulated and Empirical Infections}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates.}
\label{fig:aggregated_fit}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/incidences_by_group/age_group_rki/full_fall_baseline_new_known_case}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/incidences_by_group/age_group_rki/full_spring_baseline_new_known_case}
\end{subfigure}
\caption{Simulated and Empirical Infections by Age Group}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different age groups.}
\label{fig:age_group_fit}
\end{figure}

\begin{figure}[ht]
\centering
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/incidences_by_group/state/full_fall_baseline_new_known_case}
\end{subfigure}%
\begin{subfigure}{.6\textwidth}
  \includegraphics[width=0.9 \textwidth]{../figures/results/figures/incidences_by_group/state/full_spring_baseline_new_known_case}
\end{subfigure}
\caption{Simulated and Empirical Infections by Age Group}
\figurenotes{The figure shows the weekly incidence rates per 100,000 people for the reported versus the simulated infections rates for different federal regions.}
\label{fig:state_fit}
\end{figure}

\section{The Spread of the B117 Mutation}

\textcolor{red}{We don't have this figure in the repo yet, but the fit is perfect}
